Section_8_Team1_Lab2_Report

### 2021-08-05 notebooks/Draft_Report.Rmd
adding table sources and latest draft

We will analyze datasets pertaining to these variables for Texas counties and create three models to understand if causal relationships exist between distance traveled, population income, population density (rural or urban counties), and government regulations. Our hypothesis is that an there is a causal relationship between """

@@

```{r dataframe, echo=FALSE}
df <- read.csv('./../data/processed/covid_trips_processed.csv')
```

@@

# df %>%
#   mutate(
#     cases = log(cases+1),
#     deaths = log(deaths+1),
#     long_trip = log(long_trip),
#     density = log(density),
#     median_income=log(median_income+1),
#     unemp_rate = log(unemp_rate+1)
#   ) %>%
#   select(long_trip, cases, deaths, median_income, unemp_rate, density, pct_lt17, pct_gt65) %>%
#   GGally::ggpairs(.,
#                legend = 1,
#                aes(color = County),
#                title = "Figure 1: Variable Characterstics",
#                upper = list(continuous = wrap("cor", size = 2.5)),
#                lower = list(continuous = wrap("points", alpha = 0.5, size=0.3)),
#                diag = list(continuous = wrap("densityDiag", alpha = 0.5)),
#                columnLabels=c("Distance", "Cases", "Deaths", "Income", "Unemployment", "Pop Density", "Age < 17","Age > 65"))+
#                theme(legend.position = "bottom")

ggpairs(df, columns = 3:ncol(df), legend = 1, aes(color = County), title = "Figure 1: Variable Characterstics")
#                upper = list(continuous = wrap("cor", size = 2.5)),
#                lower = list(continuous = wrap("points", alpha = 0.5, size=0.3)),
#                diag = list(continuous = wrap("densityDiag", alpha = 0.5)))

@@

$$
  Model 1 = f(\text{log(Distance Traveled)}) = \beta_0 + \beta_1 g(\text{log(Covid-19 Cases)})  + \beta_2 h(\text{Rural County}) + \beta_3 h(\text{Median Income})
$$

$$
  Model 2 = f(\text{log(Distance Traveled)}) = \beta_0 + \beta_1 g(\text{log(Covid-19 Cases)})  + \beta_2 h(\text{Rural County}) + \beta_3 h(\text{Median Income}) + \beta_4 h(\text{Unemployment Rate}) + \beta_5 h(\text{log(Population Density})
$$

$$
  Model 3 = f(\text{log(Distance Traveled)}) = \beta_0 + \beta_1 g(\text{log(Covid-19 Cases)})  + \beta_2 h(\text{Rural County}) + \beta_3 h(\text{Median Income})
  + \beta_4 h(\text{Unemployment Rate}) + \beta_5 h(\text{log(Population Density}) + \beta_6 h(\text{log(% Age < 17}) + \beta_7 h(\text{log(% Age < 17})
$$

>>>>

We will analyze datasets pertaining to these variables for Texas counties and create three models to understand if causal relationships exist between the number of long distance trips, population income, population density (rural or urban counties). Our hypothesis is that an there is a causal relationship between """

@@

```{r dataframe, echo=FALSE}
df <- read.csv('./../data/processed/covid_trips_processed.csv')
head(df)
```

@@

df %>%
  mutate(
    cases = log(cases+1),
    deaths = log(deaths+1),
    long_trip = log(long_trip),
    density = log(density),
    median_income=log(median_income+1),
    unemp_rate = log(unemp_rate+1)
  ) %>%
  select(long_trip, cases, deaths, median_income, unemp_rate, density, pct_lt17, pct_gt65) %>%
  GGally::ggpairs(.,
               legend = 1,
               aes(color = County),
               title = "Figure 1: Variable Characterstics",
               upper = list(continuous = wrap("cor", size = 2.5)),
               lower = list(continuous = wrap("points", alpha = 0.5, size=0.3)),
               diag = list(continuous = wrap("densityDiag", alpha = 0.5)),
               columnLabels=c("Distance", "Cases", "Deaths", "Income", "Unemployment", "Pop Density", "Age < 17","Age > 65"))+
               theme(legend.position = "bottom")

# ggpairs(df, columns = 3:ncol(df), legend = 1, aes(color = County), title = "Figure 1: Variable Characterstics")
# #                upper = list(continuous = wrap("cor", size = 2.5)),
# #                lower = list(continuous = wrap("points", alpha = 0.5, size=0.3)),
# #                diag = list(continuous = wrap("densityDiag", alpha = 0.5)))

@@

$$
  Model 1 = f(\text{log(Number of Long Trips)}) = \beta_0 + \beta_1 g(\text{log(Covid-19 Cases)})  + \beta_2 h(\text{Rural County}) + \beta_3 h(\text{Median Income})
$$

$$
  Model 2 = f(\text{log(Number of Long Trips)}) = \beta_0 + \beta_1 g(\text{log(Covid-19 Cases)})  + \beta_2 h(\text{Rural County}) + \beta_3 h(\text{Median Income}) + \beta_4 h(\text{Unemployment Rate}) + \beta_5 h(\text{log(Population Density})
$$

$$
  Model 3 = f(\text{log(Number of Long Trips)}) = \beta_0 + \beta_1 g(\text{log(Covid-19 Cases)})  + \beta_2 h(\text{Rural County}) + \beta_3 h(\text{Median Income})
  + \beta_4 h(\text{Unemployment Rate}) + \beta_5 h(\text{log(Population Density}) + \beta_6 h(\text{log(% Age < 17}) + \beta_7 h(\text{log(% Age < 17})
$$
